\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage[portuges,brazil,english]{babel}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Report Title}

\author{\IEEEauthorblockN{Name Surname}
\IEEEauthorblockA{
RA \\
email address}
\and
\IEEEauthorblockN{Name Surname}
\IEEEauthorblockA{
RA \\
email address}}

\maketitle

\section{Introduction}

The introduction and motivation of the work. 

Some directions for the paper:

\begin{itemize}
	\item Figures and graphics are encouraged for making the
	report richer.
	\item {\bf The sections proposed here are not hard-constrained}. It means you can propose other sections as well as change the existing ones.
	\item Please number citations consecutively within brackets \cite{b1}. 
\end{itemize}

\section{Activities}
 
The state-of-the-art research (about prior work for solving the same problem).

\section{Proposed Solutions}

The proposed solutions for the selected problem.

\section{Experiments and Discussion}

The experiments carried out and the obtained
results.

\section{Conclusions and Future Work}

The main conclusions of the work as well as some future directions for other people interested in continuing this work. 

\begin{thebibliography}{00}
\bibitem{b1} Christopher M. Bishop. ``Pattern Recognition and Machine Learning''. Springer-Verlag New York, Inc., Secaucus, NJ, USA, 2006. 
\end{thebibliography}

\end{document}
